Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-09 main.tex
about the runtime system

>>>>

    \subsubsection{Runtime System}

    To simulate the execution of a workflow, we implemented a runtime system.
    It read the historical data and builds weights for tasks.
    These weights are then treated as the ``truth'' about the execution during the simulation.
    In the case without errors, these values are being sent to the scheduler.
    However, if errors have to be simulated, the runtime system applies a deviation function to the values.
    The deviation function computed a normally distributed deviated value, where the correct value is the mean and the deviation
    is $10\%$.
    This scenario corresponds to the real-life scenarios identified in~\cite{lotaru} and\skug{todo cite someone Jonathan cites}.

    So, the scheduler receives deviated values and makes decision based on them.
    This leads to several types of possible issues:
    \begin{itemize}
        \item Processor is blocked by another task. If the scheduler underestimated the execution time of a task, it will block another
        one from starting.
        \item The parent has not finished yet. A similar situation, but a task could start on its processor, but one or more of its parents a
        are not ready yet.
        \item Not enough memory. If the scheduler underestimated the amount of memory a task requires, this task might not be able
        to execute on a chosen processor.
        \item A task took lees than expected. We only consider this case if a task took more than 10\% less than expected. In this
        case we want to exploit the newly acquired free time by possibly starting other tasks earlier.
    \end{itemize}
